Generalizations of Quotient Inductive-Inductive Types\thanks{This work was supported by EFOP-3.6.3-VEKOP-16-2017-00002 grant and COST Action EUTypes CA15123.}

### 2019-10-15 draft/paper.tex
progress

\usepackage{proof}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{todonotes}
\input{abbrevs.tex}

@@

\newcommand{\Lift}{\Uparrow}

@@

Categories are a good example. Signatures for QIITs allow having multiple sorts,
with later ones indexed over previous ones, and equations as well. We need both
features in order to write down the signature of categories:
\begin{alignat*}{5}
  & Obj && : \Set \\
  & Mor && : Obj \ra Obj \ra \Set \\
  & id  && : Mor\,i\,j \\
  & \blank\circ\blank && : Mor\,j\,k\ra Mor\,i\,j \ra Mor\,i\,k \\
  & idl && : id \circ f = f \\
  & idr && : f \circ id = f \\
  & ass && : f \circ (g \circ h) = (f \circ g) \circ h
\end{alignat*}
The benefit of having a QIIT signature is getting a model theory ``for free'',
from the metatheory of QIITs. This model theory includes a category of algebras
which has an initial object and also some additional structure. For the
signature of categories, we get the empty category as the initial object, but it
is common to consider categories with more structure, which have more
interesting initial models.

@@

The main motivation of the current paper is to extend QIITs so that it
accommodates all algebraic notions of type theories which have been used in
previous works. As a beneficial side effect of fulfilling this goal, infinitary
QIITs such as real numbers will be covered as well.

We generalize previous notions of QIITs in the following ways:
\begin{enumerate}
  \item
  \textbf{Large constructors, large elimination} and models at different
  universe levels. This feature is routinely used in the metatheory of type
  theory, but it has not been presented explicitly in previous works about
  QIITs. In order to handle universe levels gracefully, we develop a set of
  tools, working inside an extensional type theory with \emph{algebraic
    cumulativity}.
  \item
  \textbf{Infinitary constructors}. This enables defining Cauchy real numbers
  and surreal numbers as QIITs. Also, the theory of QIIT signatures is itself
  large and infinitary, thus it can ``eat itself'', i.e.\ include its own
  signature and provide its own metatheory.  We use this self-representation to
  bootstrap the model theory of signatures, without having to assume any
  pre-existing internal syntax.
  \item
  \textbf{Recursive equations}, i.e. equations appearing as assumptions
  of constructors. These have occurred previously in syntaxes of cubical type
  theories, as boundary conditions.
  \item
  \textbf{Sort equations}, or equations between type constructors. They have
  been used recently to conveniently represent type-theoretic universes, for
  example Russell-style universes or cumulative hierarchies.
\end{enumerate}

We also develop semantics. We show that for each signature, there is a cwf
(category with families) of algebras, extended with $\Sigma$-types, an
extensional identity type and constant families. This additional structure
corresponds to a type-theoretic flavor of finite limits, and it was shown
in \cite{TODO} that the category of such cwfs is biequivalent to the category
of finitely complete categories.

As to the existence of initial algebras, we present two different term model
constructions, yielding the following statements:

@@

The reason for the two separate constructions is that sort equations are not as
well-behaved as the other extensions: they are modelled as strict equalities of
sets in algebras, and so they do not respect isomorphism of sets. We make
essential use of invariance under set isomorphism in the first term model
construction, so we cannot throw sort equations into that mix.

@@

Universe levels are usually viewed as a bureaucratic and tedious part of type
theory, and are often omitted or mentioned only in passing. Here we intend to
model universe levels in a precise way, because large eliminations are an
essential part of the practical usage of inductive types. Hence, we need a way
to conveniently reason about levels without overmuch administrative
burden. Unfortunately, simple universe setups are insufficient for this
purpose. We need two features: cumulativity and a way to quantify over finite
levels.

@@

In the most basic form, cumulativity requires that whenever $A : \Set_i$, then
also $A : \Set_{i+j+1}$. However, the $NatAlg$ example above also required a form
of cumulativity for $\Sigma$ and $\Pi$ types, and we need this in general for
QIIT algebras.

We use Sterling's cumulative algebraic type theory \cite{TODO} as the general
setting for the rest of the paper. The reason for this is twofold. First, it
supports the right kind of cumulativity for our purposes. Second, it is itself a
finitary QIIT with sort equations, hence its model theory is covered in this
paper\footnote{Which is, of course, somewhat circular, but not more circular than
  e.g.\ the study of models of ZFC in ZFC.}.

We extend the base theory with an extensional identity type and
$\Sigma$-types. In \cite{TODO} a proof of canonicity is provided for the base
theory, which also includes a standard set-theoretic model. It is
straightforward to extend the canonicity proof to cover our additional type
formers.

From now on, we refer to this theory as cETT (cumulative extensional type
theory). When working in cETT, we use conventional type-theoretic notation. We
have Russell-style universes $\Set_i$ indexed by natural numbers, dependent
functions as $(x : A)\ra B$, and dependent pairs as $(x : A)\times B$ with
projections $\proj1$ and $\proj2$. We also have a \emph{lifting} operation on
types, which introduces cumulativity. The most important rules for lifting are
the following:

\begin{figure}

Universe formation
\[
  \infer{\Gamma \vdash \Set_i : \Set_{i+j+1}}{}
\]

Type lifting
\[
%% \begin{gathered}
  \infer{\Gamma \vdash\,\Lift_j A : \Set_{i+j+1}}
        {\Gamma \vdash A : \Set_i}
%% \end{gathered}
\]
Universe lifting
\[
  \Lift_j Set_i = Set_{i+j}
\]
Term lifting
\[
\{t\,|\,\Gamma \vdash t : A\} = \{t\,|\,\Gamma \vdash t :\,\,\Lift_j A\}
\]
Context lifting
\[
(\Gamma,\,x : A) = (\Gamma,\,x :\,\Lift_j A)
\]
Function lifting
\[
\Lift_j((x : A)\ra B) = (x :\,\Lift_j A)\ra\,\Lift_j B
\]
Pair lifting
\[
\Lift_j((x : A)\times B) = (x :\,\Lift_j A)\,\times\Lift_j B
\]

\caption{Some of the rules for lifting}
\label{lifting}
\end{figure}

In Figure \ref{lifting}, we include an excerpt of Sterling's rules, with a
slight change of presentation. We use $i+j+1$ levels instead of assuming $i < j$
and lifting to $\Set_j$. We also omit rules for naturality and substitution of
lifting. In general, we can expect that lifting never impedes constructions,
because it appropriately computes out of the way.

Of special note is the \emph{term lifting rule}. It is a sort equation, an
equation between sets of terms, expressing that lifted types have exactly the
same terms as unlifted ones. This allows us to have $t :\,\,\Lift_j A$ whenever $t
: A$. Together with the universe lifting rule, this implies $A : Set_{i+j+1}$
whenever $A : Set_i$. Similarly, the lifting rules for functions and pairs give
us cumulativity for $NatAlg$.

\section{Theory of Signatures}
\label{sec:tos}

\subsection{Bootstrapping}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{todonotes}
\presetkeys{todonotes}{inline}{}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathpartir}
\usepackage{scalerel}

%% Definition env with non-italic body text
\spnewtheorem{nidefinition}[definition]{Definition}{\bfseries}{\textnormal}

@@

\input{abbrevs.tex}
\newcommand{\Lift}{\Uparrow}
\newcommand{\ToS}{\mathsf{ToS}}
\newcommand{\ext}{\triangleright}
\newcommand{\emptycon}{\scaleobj{.75}\bullet}
\newcommand{\Pii}{\mathsf{\Pi}}
\newcommand{\appi}{\mathsf{app}}
\newcommand{\lami}{\mathsf{lam}}
\newcommand{\Pie}{\mathsf{\hat{\Pi}}}
\newcommand{\appe}{\mathsf{ap\hat{p}}}
\newcommand{\lame}{\mathsf{la\hat{m}}}
\newcommand{\Piinf}{\mathsf{\tilde{\Pi}}}
\newcommand{\appinf}{\mathsf{ap\tilde{p}}}
\newcommand{\laminf}{\mathsf{la\tilde{m}}}

\newcommand{\appitt}{\mathop{{\scriptstyle @}}}

\newcommand{\Refl}{\mathsf{Refl}}

\newcommand{\IdU}{\mathsf{IdU}}
\newcommand{\ReflU}{\mathsf{ReflU}}
\newcommand{\Sig}{\mathsf{Sig}}

@@

Categories are a good example. Signatures for QIITs allow having multiple sorts,
with later ones indexed over previous ones, and equations as well. We need both
features in order to write down the signature of categories:
\begin{alignat*}{3}
  & Obj && : \Set \\
  & Mor && : Obj \ra Obj \ra \Set \\
  & id  && : Mor\,i\,j \\
  & \blank\circ\blank && : Mor\,j\,k\ra Mor\,i\,j \ra Mor\,i\,k \\
  & idl && : id \circ f = f \\
  & idr && : f \circ id = f \\
  & ass && : f \circ (g \circ h) = (f \circ g) \circ h
\end{alignat*}
The benefit of having a QIIT signature is getting a model theory ``for free'',
from the metatheory of QIITs. This model theory includes a category of algebras
which has an initial object and also some additional structure. For the
signature of categories, we get the empty category as the initial object, but it
is common to consider categories with more structure, which have more
interesting initial models.

@@

The main motivation of the current paper is to extend QIITs so that it
accommodates all algebraic notions of type theories which have been used in
previous works. As a beneficial side effect of fulfilling this goal, infinitary
QIITs such as Cauchy real numbers will be covered as well.

We generalize previous notions of QIITs in the following ways:
\begin{enumerate}
  \item
  \textbf{Large constructors, large elimination} and models at different
  universe levels. This feature is routinely used in the metatheory of type
  theory, but it has not been presented explicitly in previous works about
  QIITs. In order to handle universe levels gracefully, we work in an
  extensional type theory extended with cumulative universes.
  \item
  \textbf{Infinitary constructors}. This enables defining Cauchy real numbers
  and surreal numbers as QIITs. Also, the theory of QIIT signatures is itself
  large and infinitary, thus it can ``eat itself'', i.e.\ include its own
  signature and provide its own metatheory.  We use this self-representation to
  bootstrap the model theory of signatures, without having to assume any
  pre-existing internal syntax.
  \item
  \textbf{Recursive equations}, i.e. equations appearing as assumptions
  of constructors. These have occurred previously in syntaxes of cubical type
  theories, as boundary conditions.
  \item
  \textbf{Sort equations}, or equations between type constructors. They have
  been used recently to conveniently represent type-theoretic universes, for
  example Russell-style universes or cumulative hierarchies.
\end{enumerate}

We also develop semantics. We show that for each signature, there is a cwf
(category with families) of algebras, extended with $\Sigma$-types, extensional
identity, and constant families. This additional structure corresponds to a
type-theoretic flavor of finite limits, and it was shown in \cite{TODO} that the
category of such cwfs is biequivalent to the category of finitely complete
categories.

As to the existence of initial algebras, we present two different term model
constructions, yielding the following results:

@@

The reason for the two separate constructions is that sort equations are not as
well-behaved as the other extensions: they are modelled as strict equalities of
sets in algebras, hence they do not respect isomorphism of sets. We make
essential use of invariance under set isomorphism in the first term model
construction, so we cannot throw sort equations into that mix.

@@

Universe levels are usually viewed as a bureaucratic and tedious part of type
theory, and are often omitted or mentioned only in passing. Here we intend to
model universe levels in a precise way, because large eliminations are an
essential part of the practical usage of inductive types. Hence, we need a way
to conveniently reason about levels without too much administrative
burden. Unfortunately, simple universe setups are insufficient for this
purpose. We need two features: cumulativity and a way to quantify over finite
levels.

@@

In the most basic form, cumulativity requires that whenever $A : \Set_i$, then
also $A : \Set_{i+j+1}$. However, the $NatAlg$ example above also required a
form of cumulativity for $\Sigma$ and $\Pi$ types, which we also need in general
for QIIT algebras.

We use Sterling's cumulative algebraic type theory \cite{TODO} as the general
setting for the rest of the paper. The reason for this is twofold. First, it
supports the right kind of cumulativity for our purposes. Second, it is itself a
finitary QIIT with sort equations, hence this paper provides a model theory for
it\footnote{Which is, of course, somewhat circular, but not more circular than
  e.g.\ the study of models of ZFC in ZFC.}.

We extend the base theory with an extensional identity type, $\Sigma$-types and
the unity type. In \cite{TODO} a proof of canonicity is provided for the base
theory, which also includes a standard set-theoretic model. It is
straightforward to extend the canonicity proof to cover our additional type
formers.

From now on, we refer to this theory as cETT (cumulative extensional type
theory). When working in cETT, we use the following notation. We
have Russell-style universes $\Set_i$ indexed by natural numbers, dependent
functions as $(x : A)\ra B$, and dependent pairs as $(x : A)\times B$ with
projections $\proj1$ and $\proj2$. We also use a field projection notation
for iterated pairs. For example, for $t : (A : \Set_i) \times (B : \Set_i)
\times (f : A \ra B)$, we use $t.B$ to denote the projection of the second
component.

We write propositional equality as $t = u$, with $\refl_t$ for reflexivity. We
have equality reflection for $\blank=\blank$. The unit type is $\top$, with
inhabitant $\tt$.

We also have a lifting operation on types, which introduces cumulativity.

\begin{figure}
\begin{mathpar}
  \inferrule*[lab=universe formation]
             {\\}
             {\Gamma \vdash \Set_i : \Set_{i+j+1}}

  \inferrule*[lab=type lifting]
             {\Gamma \vdash A : \Set_i}
             {\Gamma \vdash\,\Lift_j A : \Set_{i+j+1}}

  \inferrule*[lab=universe lifting]{}{\Lift_j \Set_i = \Set_{i+j}}

  \inferrule*[lab=term lifting]
             {}
             {\{t\,|\,\Gamma \vdash t : A\} = \{t\,|\,\Gamma \vdash t :\,\,\Lift_j A\}}

  \inferrule*[lab=context lifting]
             {}
             {(\Gamma,\,x : A) = (\Gamma,\,x :\,\,\Lift_j A)}

  \inferrule*[lab=function lifting]
             {}
             {\Lift_j((x : A)\ra B) = (x :\,\Lift_j A)\ra\,\Lift_j B}

  \inferrule*[lab=pair lifting]
             {}
             {\Lift_j((x : A)\times B) = (x :\,\Lift_j A)\,\times\Lift_j B}
\end{mathpar}

\caption{Some of the rules for lifting.}
\label{lifting}
\end{figure}

In Figure \ref{lifting}, we include an excerpt of Sterling's rules, with a
slight change of presentation. We lift from $i$ to $i+j+1$ levels instead of
assuming $i < j$ and lifting to $j$. We also omit rules for naturality and
substitution of lifting. In general, we can expect that lifting never impedes
constructions, because it appropriately computes out of the way.

Of special note is the \emph{term lifting rule}. It is a sort equation, an
equation between sets of terms, expressing that lifted types have exactly the
same terms as unlifted ones. This allows us to have $t :\,\,\Lift_j A$ whenever $t
: A$. Together with the universe lifting rule, this implies $A : Set_{i+j+1}$
whenever $A : Set_i$. Similarly, the lifting rules for functions and pairs give
us cumulativity for $NatAlg$. We derive a notion of subtyping:

\begin{nidefinition}{Cumulative subtyping.}
  For $A : \Set_i$ and $B : \Set_{i+j+1}$, we define $A \prec B : \Set_{i+j+1}$
  as $B =\,\,\Lift_j A$.  It follows from term lifting and equality reflection
  that whenever $A \prec B$ and $t : A$, then also $t : B$.
\end{nidefinition}

\subsection{Universe Polymorphism}
\label{sec:universe_polymorphism}

We also need to quantify over universe levels. cETT does not support this, and
we leave it like that. Instead, for the sake of simplicity, we quantify over
levels in an unspecified metatheory \emph{outside} cETT. Hence, a universe
polymorphic cETT term is understood as a $\mathbb{N}$-indexed family of
terms. We use the $\forall$ symbol for this, e.g.\ as $\forall\,i.\,\Set_i \ra
\Set_i$. This is sufficient, because we do not need to internalize
level-polymorphic constructions in cETT.

\section{Signatures}
\label{sec:tos}

In this section, we define signatures for QIITs which support all the mentioned
generalizations. Signatures are given as contexts in a certain type theory,
called the theory of signatures. We shall abbreviate it as ToS. However, ToS
turns out to be a large infinitary QIIT itself, and we would like to define ToS
and a notion of signature without referring to QIITs, only using features
present in cETT. As a first step, we define a notion of model.

\begin{nidefinition}{Notion of model for ToS.}\label{def:tos}
For levels $i$ and $j$, there is a cETT type $\ToS_{i,j} : \Set_{\max(i,\,j)+1}$, whose elements are
ToS models (or ToS-algebras). $\ToS_{i,j}$ is an iterated $\Sigma$-type, containing
all of the following components.
\begin{enumerate}
\item
  A category with families (cwf), where all four underlying sets (of
  objects, morphisms, types and terms) are in $\Set_i$. Following notation in
  \cite{TODO}, we denote these respectively as $\Con : \Set_i$, $\Sub : \Con \ra
  \Con \ra \Set_i$, $\Ty : \Con \ra \Set_i$ and $\Tm : (\Gamma : \Con) \ra
  \Ty\,\Gamma \ra \Set_i$. We denote the empty context as $\emptycon : \Con$,
  context extension as $\blank\ext\blank : (\Gamma : \Con)\ra \Ty\,\Gamma \ra \Con$.
  Substitution on types and terms is written as $\blank[\blank]$.
\item
  A universe $\U : \Ty\,\Gamma$ with decoding $\El : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,\Gamma$.
\item
  Inductive function space, with $\Pii : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,(\Gamma\,\ext\,\El\,a) \ra \Ty\,\Gamma$, application as $\appi :
  \Tm\,\Gamma\,(\Pii\,a\,B)\ra \Tm\,(\Gamma\,\ext\,\El\,a)\,B$, and its inverse
  $\lami$.
\item
  External function space with $\Set_j$ domain: $\Pie : (A : \Set_j)\ra(A \ra
  \Ty\,\Gamma)\ra \Ty\,\Gamma$, with $\appe : \Tm\,\Gamma\,(\Pie\,A\,B)\ra(x :
  A)\ra \Tm\,\Gamma\,(B\,x)$, and likewise $\lame$ as inverse.
\item
  Infinitary function space, with $\Piinf : (A : \Set_j)\ra(A \ra
  \Tm\,\Gamma\,\U)\ra \Tm\,\Gamma\,\U$, $\appinf :
  \Tm\,\Gamma\,(\El\,(\Pie\,A\,b))\ra(x : A)\ra \Tm\,\Gamma\,(\El\,(b\,x))$, and
  $\laminf$.
\item
  An identity type $\Id : (a : \Tm\,\Gamma\,\U)\ra
  \Tm\,\Gamma\,(\El\,a)\ra\Tm\,\Gamma\,(\El\,a)\ra \Tm\,\Gamma\,\U$, with
  $\Refl : (T : \Tm\,\Gamma\,(\El\,a))\ra \Id\,a\,t\,t$ and equality reflection.
\item
  An identity type $\IdU : \Tm\,\Gamma\,\U \ra \Tm\,\Gamma\,\U \ra \Ty\,\Gamma$, with
  evident $\ReflU$ and equality reflection.
\end{enumerate}
\end{nidefinition}
In the above listing, we omit most cwf components and equations for substitution and
$\beta\eta$-conversion, but these should be understood to be also part of $\ToS_{i,j}$.

%% \paragraph{Notational conventions.}
\emph{Notational conventions.} Cwf components by default support de Bruijn
indices, which are not easily readable. We use instead a nameful notation for
binders in context extension, $\Pii$ and $\lami$, e.g.\ as $(\emptycon \ext a :
U \ext t : \El\,a)$. We also define a type-theoretic version of $\appi$ for
convenience:
\begin{alignat*}{3}
  & \blank\appitt\blank && :
      \Tm\,\Gamma\,(\Pii\,a\,B)\ra
      (u : \Tm\,\Gamma\,(\El\,a)) \ra \Tm\,\Gamma\,(B[id, u])\\
  & t\appitt u && :\equiv (\appi\,t)[id, u]
\end{alignat*}

\begin{nidefinition}{Notion of signature.}
A QIIT signature at level $j$ is a context in an arbitrary $M : \ToS_{i,j}$
model. We define the type of such signatures as follows:
\[
  \Sig_j :\equiv \forall i.\,(M : \ToS_{i,j})\ra M.Con
\]

Note that $\Sig_j$ is defined as a universe-polymorphic type, so it does not
have a type internally to cETT. A concrete signature $sig$ at level $j$ has type
$\forall i.\,(M : \ToS_{i,j})\ra M.Con$, so it builds up a context from the
components of an arbitrary $\ToS$ model.

\begin{example}
The signature for natural
numbers is the following, where $\emptycon$, $\blank\ext\blank$, $\U$, $\El$ and
$\Pii$ all refer to components of $M$:
\begin{alignat*}{3}
  & NatSig : \Sig_0 \\
  & NatSig :\equiv \lambda (M : \ToS_{i,0}). (\emptycon\,\ext\, N : \U \,\ext\, zero : \El\,N \ext suc : \Pii\,(n : N)\,(\El\,N))
\end{alignat*}
\end{example}

The $j$ level in $\Sig_j$ specifies the level of the external types appearing in
a signatures, since the $\Pie$ and $\Piinf$ function spaces have domains in $\Set_j$.
In the case of naturals numbers, no external types appear, so the level of $NatSig$
can be chosen as $0$.

With this, we are able to specify QIITs, and we can also interpret each
signature in an arbitrary ToS model, just by applying a signature to a model.
$\Sig_j$ can be viewed as a precursor to a Church-encoding for the theory of
signatures, but we only need contexts encoded in this way, and not other ToS
components. In functional programming, this encoding is sometimes called
``finally tagless''\cite{TODO}, and it is used for defining and interpreting
embedded languages.
\end{nidefinition}

\subsection{Example Signatures}

Compared to signatures in the previous work \cite{TODO}, we additionally support
$\Piinf$ and $\IdU$, and $\Id$ has a more liberal type which allows recursive
equations. Let us see examples for these three in order. For brevity, we shall
only write contexts, and assume that all ToS operations come from an arbitrary
model.

\begin{example}{Infinitary constructors}. The universe $\U$ is closed under
the $\Piinf$ function type, which makes it possible to write such functions
in the domains of $\Pii$ types. This allows a signature for $W$-types, given
arbitrary $S : \Set_i$ and $P : S \ra \Set_i$ types for shapes and positions.
\[
WSig :\equiv
\emptycon \ext W : \U \ext sup : \Pie\,S\,(\lambda s.\,\Pii\,(\Piinf\,(P\,s)\,\lambda \_.\,W) \,(\El\,W))
\]
\end{example}

\begin{example}{Sort equations}. An interesting example is the term lifting
rule for cETT (omitting everything except term lifting):
\begin{alignat*}{3}
  & cETTSig :\equiv \\
  & ...\,\ext\,Tm{\Lift} : \Pii\,(\Gamma : Con)\,(\Pii\,(A : Ty{\appitt}\Gamma)((\IdU\,(Tm{\appitt}\Gamma{\appitt}A)\,(Tm{\appitt}\Gamma{\appitt}(\Lift_j{\appitt}A))))
\end{alignat*}
\end{example}

\begin{example}{Recursive equations}. Our definition of $\Id$ returns in $\U$,
which, similarly to the case of infinitary functions, allows us to write equations
in $\Pii$ domains. A minimal example:
\[
RecEqSig :\equiv \emptycon \ext A : \U \ext a : \El\,A \ext f : \Pii\,(x : A)\,(\Pii\,(\Id\,A\,x\,a)\,(\El\,A))
\]
There more complicated and interesting examples, e.g.\ boundary conditions in
various cubical type theories\cite{TODO}. Note that our $\Id$ allows iterated
equations as well, but these are all made trivial in the semantics, where we
assume uniqueness of identity proofs.
\end{example}

\subsection{A Signature for the Theory of Signatures}

\todo{put this in infinitary term models beginning}

Starting from Section \ref{sec:infinitary_term}, we need to do proofs and
constructions by induction on signatures. However, the current signatures do not
support induction, analogously to how induction is not available for Church
encodings. We would like to have two things: a notion of signature induction,
and a model of ToS which supports induction. Then, we can use contexts in the
syntax of ToS (i.e.\ in the inductive model) as signatures. We provide a notion
of induction on signatures by
\begin{enumerate}
  \item Showing that there is a signature which describes ToS.
  \item Building categorical semantics, which for each signature provides a notion of induction.
\end{enumerate}
On the other hand, in this paper we will only \emph{assume} the existence of a
syntax for ToS starting from Section \ref{sec:infinitary_term}. We do not provide a
construction of the syntax from simpler type formers, although we do show that
lower-level ToS syntaxes are constructible from higher-level ones.
